---
title: "Stats Set Report"
author: "Caleb Smith"
date: "January 7, 2018"
output: 
  pdf_document:
    number_sections: yes
urlcolor: blue
---

# The Game

Our game is a reinterpretation of a card game titled "Set". Essentially, you attempt to match together *sets* of three cards to score points. Further instructions (and the game itself!) can be found online:

http://caleb.techhounds.com/carnival

# Probability Model

Because our game relies upon player skill to determine payout (and not just chance), our probability model is **empirical**. Video of us collecting data to create this model can be found on Google Drive, [here](). <!-- TODO add drive link -->

**Collected Data\:**

```{r, echo=FALSE}
raw <- read.csv("./src/data.csv", header=TRUE)
scores = raw$Score
scores = scores[!is.na(scores)]
print(scores, row.names=FALSE)
```

```{r, echo=FALSE}
freq = table(scores)
barplot(freq,
        main="Frequencies of Scores",
        ylab="Frequency (#)",
        xlab="Score")
```

```{r, echo=FALSE}
relfreq = freq / sum(as.vector(freq)) * 100
barplot(relfreq,
        main="Relative Frequencies of Scores",
        ylab="Relative Frequency (%)",
        xlab="Score",
        ylim=c(0,30))
```

Expected sets: $$ E(S) = `r round(mean(scores),2)` $$

SD of sets: $$ SD(S) = `r round(sd(scores),2)` $$

# Payout

Payout formula: $$ P(S) = 2 * S $$

Expected payout: $$ E(P) = `r round(2 * mean(scores),2)` $$

SD of payout: $$ SD(P) = `r round(2 * sd(scores),2)` $$

Cost to play: $10